---
title: ContDataQC Guide 02 Config"
author: "Erik.Leppo@tetratech.com"
date: "`r Sys.time()`"
output: 
  html_notebook:
    toc: yes
    depth: 3
    toc_float: no
---
# Purpose
Example code for `ContDataQC` Guide 02 Config.

# Explanation
The `ContDataQC` package contains a “configuration” file that holds the thresholds, formats, directory names, and parameter names used in the internal workings of the package.

The user has the option of loading their own configuration file to override the defaults.  

# Demo

## Vingette
```{r vignette, eval=FALSE}
library(ContDataQC)
vignette("ContDataQC_Vignette",package="ContDataQC")
```

## Open Config
Get a copy of config.R 
f

from website or in package

https://github.com/leppott/ContDataQC/blob/master/R/config.R

2. Save with new name.

3. Modify code

In this example will change 30 and 20 to 50 and 30.


4. delete other code.

5. Add comment of name and purpose.

6. Use new file in example



```{r}
# load library
# QC Raw Data
myData.Operation <- "QCRaw" #Selection.Operation[2]
myData.SiteID    <- "test2"
myData.Type      <- Selection.Type[3] #"AW"
myData.DateRange.Start  <- "2013-01-01"
myData.DateRange.End    <- "2014-12-31"
myDir.import <- file.path(myDir.BASE,Selection.SUB[1]) #"Data1_RAW"
myDir.export <- file.path(myDir.BASE,Selection.SUB[2]) #"Data2_QC"
myReport.format <- "html"
ContDataQC(myData.Operation, myData.SiteID, myData.Type, myData.DateRange.Start
           , myData.DateRange.End, myDir.import, myDir.export
           , fun.myReport.format=myReport.format)
```

Re run with different thresholds.

```{r}
# QC Raw Data
myData.Operation <- "QCRaw" #Selection.Operation[2]
myData.SiteID    <- "test2"
myData.Type      <- "AW" #Selection.Type[3] 
myData.DateRange.Start  <- "2013-01-01"
myData.DateRange.End    <- "2014-12-31"
myDir.import <- file.path(myDir.BASE, "Data1_RAW") #Selection.SUB[1]
myDir.export <- file.path(myDir.BASE, "Data2_QC") #Selection.SUB[2]
myReport.format <- "html"
myConfig        <- "config_flat.R"
ContDataQC(myData.Operation, myData.SiteID, myData.Type, myData.DateRange.Start
           , myData.DateRange.End, myDir.import, myDir.export
           , fun.myReport.format=myReport.format)
```

