---
title: ContDataQC Guide 01 Basic Functions
author: "Erik.Leppo@tetratech.com"
date: "`r Sys.time()`"
output: 
  html_notebook:
    toc: yes
    depth: 3
    toc_float: no
---
# Purpose
Example code for `ContDataQC` Guide 03 Basic Functions

# Explanation
The `ContDataQC` package contains many functions.  This is an overview of the core (basic) functions.

# Purpose of Package
The package was designed to help users handle basic Quality Control (QC) of their continuous data logger information.

# Help
Help files are built into the code for each function.

## Vingette
The vignette pulls together all of the help examples into a single document.
```{r Help_Vignette, eval=FALSE}
library(ContDataQC)
vignette("ContDataQC_Vignette",package="ContDataQC")
```

## List of All Functions

```{r Help_Index, eval=FALSE}
library(ContDataQC)
help(package="ContDataQC")
```

List of all objects in package.
```{r PackageListObjects, echo=TRUE}
ls("package:ContDataQC")
```

# Basic Functions
Examples can be accessed from the help index (above) or with the help search function "?" (see code below).

## ContDataQC
The ContDataQC function takes as input a data frame of continuous data.  Most data loggers will output such a file.  The examples use the output from Hobo data loggers.

The function can perform multiple sub-function that are intended to be run in sequence.

* GetGageData
    + Downloads to a file continuous data from USGS gages. 
* QCRaw
    + Applies basic QC checks on unmodified data.
* Aggregate
   +  This function is used to create a single file with a specified date range.  It combines data from multiple files and/or trims data from files. 
   + These files can then be used for summary statistics.
* SummaryStats
    + Generates outputs of basic statistics for the given file.

The output of each sub-function is different but is generally a new data file and a QC Report.

The QCRaw, Aggregate, and SummaryStats functions are intended to be run on a directory of files and the function performs operations based on the function inputs and file names.  However, there are "file" versions of the same functions that will work on a vector of filenames.

```{r Example_ContDataQC, eval=FALSE}
library(ContDataQC)
?ContDataQC
```

All of the examples use data files that ship with the package but they also assume that certain directories are on the user's computer.

* Data1_RAW
* Data2_QC
* Data3_Aggregate
* Data4_SummaryStats

It is also intended that users proceed from one step to the next.  For advanced users it is possible to skip steps but your data must be in the expected format for the functions to work as intended.

To create the directories and example data run the code below.

```{r Example_SetUp, eval=FALSE}
# Examples of each operation

# Parameters
Selection.Operation <- c("GetGageData","QCRaw", "Aggregate", "SummaryStats")
Selection.Type      <- c("Air","Water","AW","Gage","AWG","AG","WG")
Selection.SUB <- c("Data1_RAW","Data2_QC","Data3_Aggregated","Data4_Stats")
myDir.BASE <- getwd()

# Create data directories
myDir.create <- paste0("./",Selection.SUB[1])
  ifelse(dir.exists(myDir.create)==FALSE,dir.create(myDir.create),"Directory already exists")
myDir.create <- paste0("./",Selection.SUB[2])
  ifelse(dir.exists(myDir.create)==FALSE,dir.create(myDir.create),"Directory already exists")
myDir.create <- paste0("./",Selection.SUB[3])
  ifelse(dir.exists(myDir.create)==FALSE,dir.create(myDir.create),"Directory already exists")
myDir.create <- paste0("./",Selection.SUB[4])
  ifelse(dir.exists(myDir.create)==FALSE,dir.create(myDir.create),"Directory already exists")

# Save example data (assumes directory ./Data1_RAW/ exists)
myData <- data_raw_test2_AW_20130426_20130725
  write.csv(myData,paste0("./",Selection.SUB[1],"/test2_AW_20130426_20130725.csv"))
myData <- data_raw_test2_AW_20130725_20131015
  write.csv(myData,paste0("./",Selection.SUB[1],"/test2_AW_20130725_20131015.csv"))
myData <- data_raw_test2_AW_20140901_20140930
  write.csv(myData,paste0("./",Selection.SUB[1],"/test2_AW_20140901_20140930.csv"))
myData <- data_raw_test4_AW_20160418_20160726
  write.csv(myData,paste0("./",Selection.SUB[1],"/test4_AW_20160418_20160726.csv"))
myFile <- "config.TZ.Central.R"
  file.copy(file.path(path.package("ContDataQC"),"extdata",myFile)
            ,file.path(getwd(),Selection.SUB[1],myFile))
```

### GetGageData
Download USGS gage data for a specified time period.
```{r Example_GetGageData, eval=FALSE}
myDir.BASE <- getwd()
# Get Gage Data
myData.Operation    <- "GetGageData" #Selection.Operation[1]
myData.SiteID       <- "01187300" # Hubbard River near West Hartland, CT
myData.Type         <- "Gage" #Selection.Type[4]
myData.DateRange.Start  <- "2013-01-01"
myData.DateRange.End    <- "2014-12-31"
myDir.import <- ""
myDir.export <- file.path(myDir.BASE, "Data1_RAW") #Selection.SUB[1]
ContDataQC(myData.Operation, myData.SiteID, myData.Type, myData.DateRange.Start
          , myData.DateRange.End, myDir.import, myDir.export)
```

### QCRaw
Apply flags to data based on QC tests.
```{r Example_QCRaw, eval=FALSE}
myDir.BASE <- getwd()
# QC Raw Data
myData.Operation <- "QCRaw" #Selection.Operation[2]
myData.SiteID    <- "test2"
myData.Type      <- "AW" #Selection.Type[3]
myData.DateRange.Start  <- "2013-01-01"
myData.DateRange.End    <- "2014-12-31"
myDir.import <- file.path(myDir.BASE, "Data1_RAW") #Selection.SUB[1]
myDir.export <- file.path(myDir.BASE, "Data2_QC")  #Selection.SUB[2]
myReport.format <- "docx"
ContDataQC(myData.Operation, myData.SiteID, myData.Type, myData.DateRange.Start
           , myData.DateRange.End, myDir.import, myDir.export
           , fun.myReport.format=myReport.format)
```

### Aggregate
Combine or split data based on date range.
```{r Example_Aggregate, eval=FALSE}
myDir.BASE <- getwd()
# Aggregate Data
myData.Operation <- "Aggregate" #Selection.Operation[3]
myData.SiteID    <- "test2"
myData.Type      <- "AW" #Selection.Type[3] 
myData.DateRange.Start  <- "2013-01-01"
myData.DateRange.End    <- "2014-12-31"
myDir.import <- file.path(myDir.BASE, "Data2_QC") #Selection.SUB[2]
myDir.export <- file.path(myDir.BASE, "Data3_Aggregated") #Selection.SUB[3]
#Leave off myReport.format and get default (html).
ContDataQC(myData.Operation, myData.SiteID, myData.Type, myData.DateRange.Start
           , myData.DateRange.End, myDir.import, myDir.export)
```

### SummaryStats
Calculate statistics.
```{r Example_SummaryStats, eval=FALSE}
myDir.BASE <- getwd()
# Summary Stats
myData.Operation <- "SummaryStats" #Selection.Operation[4]
myData.SiteID    <- "test2"
myData.Type      <- "AW" #Selection.Type[3]
myData.DateRange.Start  <- "2013-01-01"
myData.DateRange.End    <- "2014-12-31"
myDir.import <- file.path(myDir.BASE, "Data3_Aggregated") # Selection.SUB[3]
myDir.export <- file.path(myDir.BASE, "Data4_Stats") # Selection.SUB[4]
#Leave off myReport.format and get default (html).
ContDataQC(myData.Operation, myData.SiteID, myData.Type, myData.DateRange.Start
          , myData.DateRange.End, myDir.import, myDir.export)
```

