---
title: ContDataQC Guide 01 Intro
author: "Erik.Leppo@tetratech.com"
date: "`r Sys.time()`"
output: 
  html_notebook:
    toc: yes
    depth: 3
    toc_float: no
---
# Purpose
Example code for `ContDataQC` Guide 01 Intro

# Explanation
The `ContDataQC` package contains many functions.  This is a brief introdution to them.

# Purpose of Package
The package was designed to help users handle basic Quality Control (QC) of their continuous data logger information.

# Help
Help files are built into the code for each function.

## Vingette
The vignette pulls together all of the help examples into a single document.
```{r Help_Vignette, eval=FALSE}
library(ContDataQC)
vignette("ContDataQC_Vignette",package="ContDataQC")
```

## List of All Functions

```{r Help_Index, eval=FALSE}
library(ContDataQC)
help(package="ContDataQC")
```

List of all objects in package.
```{r PackageListObjects, echo=TRUE}
ls("package:ContDataQC")
```
# Functions
Examples can be accessed from the help index (above) or with the help search function "?" (see code below).

## ContDataQC
The ContDataQC function takes as input a data frame of continuous data.  Most data loggers will output such a file.  The examples use the output from Hobo data loggers.

The function can perform multiple sub-function that are intended to be run in sequence.

* GetGageData
    + Downloads to a file continuous data from USGS gages. 
* QCRaw
    + Applies basic QC checks on unmodified data.
* Aggregate
   +  This function is used to create a single file with a specified date range.  It combines data from multiple files and/or trims data from files. 
   + These files can then be used for summary statistics.
* SummaryStats
    + Generates outputs of basic statistics for the given file.

The output of each sub-function is different but is generally a new data file and a QC Report.

The QCRaw, Aggregate, and SummaryStats functions are intended to be run on a directory of files and the function performs operations based on the function inputs and file names.  However, there are "file" versions of the same functions that will work on a vector of filenames.

```{r Example_ContDataQC, eval=FALSE}
library(ContDataQC)
?ContDataQC
```

## CompSiteCDF
Takes as an input a data frame with Data and SiteID and up to 8 columns of parameter data. Values are daily means for some measurement.

CDFs are generate for all data, year, season, and year/season and saved to a PDF. Winter + Year is such that December is included with the following year (e.g., Dec 2013, Jan 2014, Feb 2014 are 2014Winter).

Two plots per page are generated. The first plot is the proportion of values at a certain value. This plot is similar to a histogram. The second plot is a CDF of values. The line represents the proportion of values less than or equal to parameter values on the x-axis.
```{r Example_CompSiteCDF, eval=FALSE}
library(ContDataQC)
?CompSiteCDF
```

## Export.IHA
Creates a date frame (and file export) from Continuous Data in the format used by the `IHA` package.

The `IHA` package is not included in the `ContDataQC` package. But an example is provided.  To run the example IHA calculations you will need the `IHA` package (from GitHub) and for the example export the `XLConnect` packages Install commands in the example.

https://github.com/jasonelaw/iha
```{r Example_Export.IHA, eval=FALSE}
library(ContDataQC)
?Export.IHA
```

## Export.StreamThermal
Creates a date frame (and file export) from Continuous Data in the format used by the `StreamThermal` package. 

Required fields are StationID, Date, dailyMax, dailyMin, and dailyMean. The fields are named "siteID", "Date", "MaxT", "MinT", and "MeanT".

The `StreamThermal` package is available on GitHub. It can be installed withe the `devtools` package.

https://github.com/tsangyp/StreamThermal
```{r Example_Export.StreamThermal, eval=FALSE}
library(ContDataQC)
?Export.StreamThermal
```

## PeriodStats
Generates daily stats (N, mean, min, max, range, std deviation) for the specified time period before a given date. Output is a multiple column CSV (Date and Parameter Name by statistic) and a report (HTML or DOCX) with plots. Input is the ouput file of the QC operation of ContDataQC().
```{r Example_PeriodStats, eval=FALSE}
library(ContDataQC)
?PeriodStats
```

## rarify
This function subsamples (rarifies) a 3 column data frame (SampleID, TaxonID, Count) to a fixed count per sample.  

The function returns a data frame with the same three columns but the abund field has been modified so the total count for each sample is no longer above the target (subsiz).
```{r Example_rarify, eval=FALSE}
library(ContDataQC)
?rarify
```

## RBIcalc
Calculates the Richards-Baker (Flashiness) Index (RBI) from a vector of mean daily flows.  The return is a value that represents the RBI for the input data.

```{r Example_RBI, eval=FALSE}
library(ContDataQC)
?RBIcalc
```


