---
title: ContDataQC Guide 04 Gage Data
author: "Erik.Leppo@tetratech.com"
date: "`r Sys.time()`"
output: 
  html_notebook:
    toc: yes
    depth: 3
    toc_float: no
---
# Purpose
Example code for `ContDataQC` Guide 04 Gage Data

# Demo


## Load Library
```{r LoadLibrary, eval=FALSE}
# load library
library(ContDataQC)
# help file to get code
?ContDataQC
```

## Example Data
If don't have your own data you can copy data saved in the package.  The code below sets up some directories and 
```{r ExampleData, eval=FALSE}
# Parameters
Selection.Operation <- c("GetGageData","QCRaw", "Aggregate", "SummaryStats")
Selection.Type      <- c("Air","Water","AW","Gage","AWG","AG","WG")
Selection.SUB <- c("Data1_RAW","Data2_QC","Data3_Aggregated","Data4_Stats")
myDir.BASE <- getwd()

# Create data directories
myDir.create <- paste0("./",Selection.SUB[1])
  ifelse(dir.exists(myDir.create)==FALSE,dir.create(myDir.create),"Directory already exists")
myDir.create <- paste0("./",Selection.SUB[2])
  ifelse(dir.exists(myDir.create)==FALSE,dir.create(myDir.create),"Directory already exists")
myDir.create <- paste0("./",Selection.SUB[3])
  ifelse(dir.exists(myDir.create)==FALSE,dir.create(myDir.create),"Directory already exists")
myDir.create <- paste0("./",Selection.SUB[4])
  ifelse(dir.exists(myDir.create)==FALSE,dir.create(myDir.create),"Directory already exists")

# Save example data (assumes directory ./Data1_RAW/ exists)
myData <- data_raw_test2_AW_20130426_20130725
  write.csv(myData,paste0("./",Selection.SUB[1],"/test2_AW_20130426_20130725.csv"))
myData <- data_raw_test2_AW_20130725_20131015
  write.csv(myData,paste0("./",Selection.SUB[1],"/test2_AW_20130725_20131015.csv"))
myData <- data_raw_test2_AW_20140901_20140930
  write.csv(myData,paste0("./",Selection.SUB[1],"/test2_AW_20140901_20140930.csv"))
myData <- data_raw_test4_AW_20160418_20160726
  write.csv(myData,paste0("./",Selection.SUB[1],"/test4_AW_20160418_20160726.csv"))
myFile <- "config.TZ.Central.R"
  file.copy(file.path(path.package("ContDataQC"),"extdata",myFile)
            ,file.path(getwd(),Selection.SUB[1],myFile))
```

## Get Gage Data
Request 2 years of data (calendar years 2013 and 2014) for one gage (01187300, Hubbard River near West Hartland, CT).

https://waterdata.usgs.gov/usa/nwis/uv?01187300

```{r GetGageData, eval=FALSE}
library(ContDataQC)
# Set parameter
myDir.BASE          <- getwd()
myData.Operation    <- "GetGageData" #Selection.Operation[1]
myData.SiteID       <- "01187300" # Hubbard River near West Hartland, CT
myData.Type         <- "Gage" #Selection.Type[4]
myData.DateRange.Start  <- "2013-01-01"
myData.DateRange.End    <- "2014-12-31"
myDir.import <- ""
myDir.export <- file.path(myDir.BASE, "Data1_RAW")
# Run the function
ContDataQC(myData.Operation, myData.SiteID, myData.Type, myData.DateRange.Start
          , myData.DateRange.End, myDir.import, myDir.export)
```

To get different gages change the SiteID.

To get different time periods change the start and end dates.  Dates must be in the ISO standard format of YYYY-MM-DD (4 digit year, 2 digit month, 2 digit day, and dash separators).

The import directory is not needed for this function so it can be left blank.

The export directory is where the data download will be saved.

Directories can be entered using the file.path function.

### Gage Data, Different Timezone
At times you will need to download data from different time zones (TZ).  ContDataQC relies on the USGS `dataRetrieval` package to get USGS gage data.  This package converts time from UTC (think Grenwich mean time) into your local time zone on your PC.  If you download data for a different time zone the times will be "off".  The `ContDataQC` gets around this by using a parameter in a configuration file.  You can include a custom config file when requesting data.  Just add a variable for fun.myConfig.

In the example below change from US Eastern TZ to US Central TZ.
```{r GetGageData_TZ, eval=FALSE}
library(ContDataQC)
# Set parameter
myDir.BASE          <- getwd()
myData.Operation    <- "GetGageData" #Selection.Operation[1]
myData.SiteID       <- "07032000" # Mississippi River at Memphis, TN
myData.Type         <- Selection.Type[4] #"Gage"
myData.DateRange.Start  <- "2013-01-01"
myData.DateRange.End    <- "2014-12-31"
myDir.import <- ""
myDir.export <- file.path(myDir.BASE, Selection.SUB[1])
# include path if not in working directory
myConfig            <- file.path(getwd(),Selection.SUB[1],"config.TZ.central.R")
ContDataQC(myData.Operation, myData.SiteID, myData.Type, myData.DateRange.Start
           , myData.DateRange.End, myDir.import, myDir.export, myConfig)
```

